Out-of-Sample Comparisons of Overfit Models

### 2014-03-21 paper.tex
Preamble: remove headers and clean up unused commands

\section{Monte Carlo}\label{sec:mc}
\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}} This
section presents two simulations that investigate the accuracy of our
theory in small samples.\footnote{Simulations were conducted in R
  \citep{Rde:10} using Sweave \citep{Lei:02} and the Lattice
  \citep{Sar:10}, RSQLite \citep{Jam:10}, tikzDevice
  \citep{ShB:11:0.6.1}, and pgfSweave \citep{BrS:11:1.2.1} packages.}
The first looks at the asymptotic normality of the DMW statistic
centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
section's results imply that centering on the first should give an
approximately normal statistic and centering on the second should give
a normal statistic when $P$ is small relative to $T$.  The second
simulation looks at the size and power of several statistics when
conducting inference about the difference in the models'
generalization error.  For all of the simulations, we look at
fixed-window OOS tests to speed up computation time.

>>>>

\section{Monte Carlo}
\label{sec:mc}

This section presents two simulations that investigate the accuracy of
our theory in small samples.%
\footnote{Simulations were conducted in R \citep{Rde:10} using Sweave
  \citep{Lei:02} and the Lattice \citep{Sar:10}, RSQLite
  \citep{Jam:10}, and tikzDevice \citep{ShB:11:0.6.1} packages.} %
The first looks at the asymptotic normality of the DMW statistic
centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
section's results imply that centering on the first should give an
approximately normal statistic and centering on the second should give
a normal statistic when $P$ is small relative to $T$.  The second
simulation looks at the size and power of several statistics when
conducting inference about the difference in the models'
generalization error.  For all of the simulations, we look at
fixed-window OOS tests to speed up computation time.
